Kyoto VR MQP Paper First Draft

### 2019-09-23 paper.tex
start introduction

\usepackage{lipsum}   % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
%\usepackage{minted}
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric]{biblatex}
\usepackage[page, titletoc, title]{appendix}
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref}      % hyperlinks

@@

>>>>

\usepackage{lipsum}   % lorem-ipsum placeholder text
\usepackage{bookmark} % links to other parts of the PDF
%\usepackage{minted}
% if we want to use a different style, here are some to look at
% https://www.overleaf.com/learn/latex/Biblatex_bibliography_styles
\usepackage[backend=biber,style=numeric,sorting=none]{biblatex}
\usepackage[page, titletoc, title]{appendix}
\usepackage[margin=1in]{geometry} % set 1in margins
\usepackage{hyperref}      % hyperlinks

@@

The field of consumer-oriented Augmented Reality (AR) technology is just coming
into full swing, and it presents many unique opportunities for a myriad of
fields. This budding technological platform uses digital displays to augment
real-world information with computer-generated data. As the technology
progresses several disparate industries have found novel uses for it, some
becoming extremely profitable~\autocite{webster2018}. With smartphone
manufacturers investing billions into AR technology~\autocite{mason2016}, it
seems poised to be the next big digital interface.

Tourism and art are among the fields that could gain the most from AR
technology~\autocite{saenz2009, katz2018}.
